Topological Equivariant Artist Model

### 2022-01-10 slides/main.tex
monoidal category

\begin{frame}{Equivariant Artist}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        {\mathcal{O}_{K, E}} 
        \arrow[r, "A"] 
        \arrow[d, "\varphi"'] \& 
        {\mathcal{O}_{S,H}} 
        \arrow[d, "\varphi_H"] \\
        {\mathcal{O}_{K^{\prime}, E^{\prime}}} 
        \arrow[r, "A"]    \& 
        {\mathcal{O}_{S^{\prime}, H^{\prime}}}    
        \end{tikzcd} 
    \end{equation*}
\begin{block}
    \vartistc\ is equivariant when there exists a $\dfuncc_H$ s.t the diagram commutes. 
    \begin{equation}

    \end{equation}
\end{block}
    \end{frame}

\begin{frame}{More than one field?}
    %cartestian categories
\end{frame}

>>>>

\begin{frame}{Equivariant Artist}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        {\mathcal{O}_{K, E}} 
        \arrow[r, "A"] 
        \arrow[d, "\varphi"'] \& 
        {\mathcal{O}_{S,H}} 
        \arrow[d, "\varphi_H"] \\
        {\mathcal{O}_{K^{\prime}, E^{\prime}}} 
        \arrow[r, "A"]    \& 
        {\mathcal{O}_{S^{\prime}, H^{\prime}}}    
        \end{tikzcd} 
    \end{equation*}
        \begin{block}
            \vartistc\ is equivariant when there exists a $\dfuncc_H$ s.t the diagram commutes. 
            \begin{equation*}
            \end{equation*}
        \end{block}
    \end{frame}

\begin{frame}{More than one field?}
    \begin{block}{} 
        \label{def:category:F} The fiber category $\mathcal{\dfiberc}$ is a monoidal category\cite{milewskiCategoryTheoryProgrammers}, which means it is a category equipped with a bifunctur $\otimes: \mathcal{\dfiber} \times \mathcal{\dfiber} \rightarrow \mathcal{\dfiber}$
        \begin{itemize}
          \item \textit{object} a monoid object \dfiber. A monoid is a set with a binary operator that is associative, closed, and for which the set contains an identity element $i$ \cite{nlab:monoid}.
          \item \textit{morphisms} $\dfiber \otimes \dfiber \rightarrow \dfiber$ and unit $i \rightarrow \dfiber$
        \end{itemize}
    \end{block}
\end{frame}
